Introduction of using AWS instance to run experiments

### 2022-03-03 docs/run_experiments.Rmd
Update some default args

@@

```
python hrlcm/fit_compose_lr.py --exp_name unet_k15_only_clr_220epc --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --epochs 201
```

>>>>

Before official running, test a bit about the largest values of `num_worker`, `train_batch_size`, `val_batch_size` that could be used. For `g5.12xlarge`, these values could be:

- `num_worker`:48
- `train_batch_size`: 32 (could be a bit bigger, but it is recommended to use $2^n$)
- `val_batch_size`: 32

Also, test the optimal learning rate and scheduler to use:

- 0.1 is too large.
- 0.01 is too large.
- 0.001 is a good start point.
- 0.00001 is a good end point.

`final_lr` for `optim.AdaBound`:

- 0.01 still works fine.

Syntax:

@@

```
python hrlcm/fit_compose_lr.py --exp_name unet_all_norm_200 --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.000001 --max_lr 0.00001 --save_freq 20 --epochs 201
```
